### 2013-07-24 doc/asplos14/evaluation.tex
don't rotate concurrent plot
rest of characterization data

\begin{table}[htb]
\small
\begin{center}
\setlength{\tabcolsep}{1pt}
\begin{tabular}{l|c|c|c|c|c}
% remember: bfs time is mean_time * nbfs
                               &   GUPS            &   BFS   & IntSort & UTS & Pagerank \\ \hline
App. message rate/core (K/s)  & 984            &  983   &      &     \\
%Application message bytes     & 31.8 $\pm$ 1.2    & \\
Avg. App. message bytes & 31.8              & 33.9    &      & \\
Network BW per node (MB/s)    & 478           & 511 &    &      \\
%Network message bytes         & 23.2K $\pm$ 12.4K & \\ \hline
Avg. Network message bytes     & 23.2K             & 4.3K    & &    \\ \hline
Avg. active tasks/core         & 0.9               & 58.2    &  &  \\
Max. active tasks/core         & 1                 & 128     &  &   \\
Avg. ready queue length/core   & 2.3               & 6.1     &  &    \\
Avg. Ctx switch rate/core (K/s) & 34.2           & 539  &     &  \\ 
Steal count                    & 0                 & 0       &  &     \\
\end{tabular}
\end{center}
\caption{Internal runtime metrics, for 64-node, 16-core-per-node benchmark runs}
\label{tab:grappa-metrics}
\end{table}

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[height=0.5\textwidth, angle=90]{results/plot_concurrency.pdf}
    \end{center}
    \vspace*{-0.25in}
    \caption{Throughput, request latency, and idleness as number of concurrent workers is varied}
    \label{fig:grappa-concurrency}
\end{figure}

>>>>

\begin{table}[htb]
\small
\begin{center}
\setlength{\tabcolsep}{1pt}
\begin{tabular}{l|c|c|c|c|c}
% remember: bfs time is mean_time * nbfs
                                &  GUPS  &  BFS & IntSort &   UTS & Pagerank \\ \hline
App. message rate/core (K/s)    & 984    &  983 &     732 &   411 &      474 \\
Avg. App. message bytes         & 31.8   & 33.9 &    30.6 &  47.3 &     45.5 \\
Network BW per node (MB/s)      & 478    & 511  &     343 &   298 &      332 \\
Avg. Network message bytes      & 23.2K  & 4.3K &   12.8K &  4.2K &     3.0K \\ \hline
Avg. active tasks/core          & 0.9    & 58.2 &     0.9 & 326.2 &    429.3 \\
Max. active tasks/core          & 1      & 128  &       1 &   507 &     1024 \\
Avg. ready queue length/core    & 2.3    & 6.1  &     1.3 & 186.1 &    300.4 \\
Avg. Ctx switch rate/core (K/s) & 34.2   & 539  &     127 &   543 &      336 \\ 
Steal attempts/core/s           & 0      & 0    &       0 &  54.4 &        0 \\
Steal successes/core/s          & 0      & 0    &       0 &  17.0 &        0 \\
\end{tabular}
\end{center}
\caption{Internal runtime metrics, for 64-node, 16-core-per-node benchmark runs}
\label{tab:grappa-metrics}
\end{table}

@@

\begin{figure}[ht]
    \begin{center}
      % \includegraphics[height=0.5\textwidth, angle=90]{results/plot_concurrency.pdf}
      \includegraphics[height=0.4\textwidth]{results/plot_concurrency.pdf}
    \end{center}
    \vspace*{-0.25in}
    \caption{Throughput, request latency, and idleness as number of concurrent workers is varied}
    \label{fig:grappa-concurrency}
\end{figure}
